Switch equivalence and weak prime domains for fusions

### 2023-10-13 fusione.tex
cose

@@

To proceed further, we have to introduce a notion from general category theory.

\begin{definition}[\cite{borceux1994handbook1,adamek1994locally}]
Let $\X$ be a category, a \emph{separating family},  is a class $\mathcal{S}$ of objects such that, for every pair of arrows $f, g:X\rightrightarrows Y$, if \[f\circ s = g\circ s\] for every $s:S\to X$ with domain $S\in \mathcal{S}$, then $f=g$.

Given a separating family $\mathcal{S}$, we will say that a morphism $f:X\to Y$,  is an \emph{$\mathcal{S}$-surjection} if for every $s:S\to Y$ with domain in $\mathcal{S}$  there exists $s':S\to X$ such that $f\circ s'= s$.
\end{definition}

We can list some examples of separating families.

\begin{example}
	contenuto...
\end{example}
\begin{example}
	contenuto...
\end{example}
\begin{example}
	contenuto...
\end{example}
\begin{example}
	contenuto...
\end{example}
\begin{proposition}
Let $f:X\to Y$ be a morphism in a category $\X$ with a separating family $\mathcal{S}$, then every $\mathcal{S}$-surjection is an epimorphism.
\end{proposition}
\begin{proof}
	Let $f:X\to Y$ be an $\mathcal{S}$-surjection, and suppose that there exist two arrows $g, h:Y\rightrightarrows Z$ such that 
	\[g\circ f = h\circ f\]
Since $f$ is an $\mathcal{S}$-surjection, for every $S\in \mathcal{S}$ and arrow $s:S\to Y$ there exists $s':S\to X$ such that $f\circ s'=s$, so that
\begin{align*}
	g\circ s &= g\circ f \circ s'\\&=h\circ f \circ s'\\&= h\circ s
\end{align*} 
	The thesis now follows since $\mathcal{S}$ is separating.	 \qed 
\end{proof}

@@

\begin{lemma} Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that $\X$ has a separator $\mathcal{S}$. Consider two consistent permutation $\sigma,\sigma':[0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$. Suppose that $\sigma\neq \sigma'$ and let $j$ be the minimum index such that $\sigma(j)\neq \sigma'(j)$. Let also $r(\der{D})$ be $\{\rho_i\}_{i=0}^n$. Then the following hold true:
	\begin{enumerate}
		\item if $j=0$, then the rule $\rho_0$ is not consuming;
		\item if $j\neq 0$, then the rule $\rho_{j-1}$ is not consuming.
	\end{enumerate}
\end{lemma}
\begin{proof}\begin{enumerate}
		\item 
		\item  \qed
	\end{enumerate}
\end{proof}

\begin{corollary}\label{cor:unique}
Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming. Given two non-empty derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$, if $\X$ has a separator $\mathcal{S}$, then there exists at most one consistent permutation between them.
\end{corollary}

\begin{lemma}Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming. Given two non-empty derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$, if $\X$ has a separator $S$, then there exists at most one consistent permutation between them.
\end{lemma}

\begin{proof} Consider two consistent permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$ and let $\xi, \xi':\tpro{D}\rightrightarrows \lpro \der{D}' \rpro$ be the associated isomorphisms.	\[\xymatrix@C=8pt@R=20pt{ &&&&&R_{i}\ar@/^1.4cm/[dddrrr]^{h'_{\sigma(i)}} \ar@/_1.7cm/[dddlll]_{h'_{\sigma'(i)}}|(.65)\hole|(.83)\hole\ar[ddd]|(.35)\hole^{h_i}|(.805)\hole\\&&&&K_i \ar@/_1.7cm/[dddlll]_{k'_{\sigma'(i)}}|(.67)\hole\ar[dl]_{l_i} \ar[ur]^{r}\ar@/^1.4cm/[dddrrr]^{k'_{\sigma(i)}} \ar[ddd]|(.35)\hole_(.7){k_i}\\&&&L_i\ar@/_1.7cm/[dddlll]_{m'_{\sigma'(i)}}\ar@/^1.4cm/[dddrrr]^(.7){m'_{\sigma(i)}} \ar[ddd]_{m_i}\\&&G'_{\sigma'(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma'(i)+1}}}&&&G_{i+1}  \ar@/^.5cm/[dddl]^{\iota_{G_{i+1}}}&&& G'_{\sigma(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D'_{\sigma'(i)}\ar[ur]^{g'_{\sigma'(i)}}\ar[dl]_(.35){f'_{\sigma'(i)}}\ar[dd]^{\iota_{D'_{\sigma'(i)}}}&&&D_i \ar[dd]^{\iota_{D_i}}\ar[ur]^{g_i}  \ar[dl]_{f_i}&&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_(.4){f'_{\sigma(i)}}\\ G'_{\sigma'(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G_{\sigma'(i)}}}&&&G_i \ar@/_.3cm/[dr]_(.35){\iota_{G_i}} &&& G'_{\sigma(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G'_{\sigma(i)}}}\\&\lpro \der{D}'\rpro &&& \tpro{D} \ar[rrr]_{\xi} \ar[lll]^{\xi'}&&& \lpro \der{D}' \rpro}\]

Suppose that there exists $j\in n+1$ be such that $\sigma(j)\neq \sigma'(j)$.  Let $k$ be $\sigma^{-1}(\sigma'(i))$, then, in particular $j\neq k$. By \Cref{rem:coproj} we know that
\begin{align*}
\iota_{L_{k}}=\xi^{-1} \circ \iota'_{L_{\sigma(k)}}
\end{align*}We have two cases.
	\begin{itemize}
		\item $i< \sigma^{-1}(\sigma'(i))$.
		\item $\sigma^{-1}(\sigma'(i))<i$.\qed 
	\end{itemize} 
\end{proof}

\begin{proof}  whithout loss of generality we can suppose that $\sigma'(i)<\sigma(i)$. Using consistency, we get a diagram

	Take an arrow $s:S\to L_i$ , then we 
\end{proof}

@@

\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists. If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
\end{definition}

@@

\begin{example}
	\todo{pensare ad un esempio in cui l'indipendenza non basta (o farsi venire in mente una dimostrazione della prop. 13 della versione su arxiv)}
\end{example}

@@

We can prove some other properties of the arrows appearing in the diagram above.
\begin{itemize}
	\item The three rectangles below are pushouts and their left halves are pushouts too. Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{g}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j'}&Q' \ar[r]^{t} & T}\]
\end{itemize}
\end{remark}

@@

	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
\begin{definition}
	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive. Given two switchable direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, with a filler $(u,u')$, we can define other two direct derivations $S_{u,u'}(\dder{D}'):G\Mapsto J$ and $S_{u,u'}(\dder{D}):J\Mapsto T$ as follows:
		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{u,u'}(\dder{D}')\cdot S_{u,u'}(\dder{D})$.
\end{definition}

@@

\subsection{Proper switchability is global}

\begin{lemma}
	contenuto...
\end{lemma}
\begin{proof}
	contenuto... \qed 
\end{proof}

\todo{NO IDEA PER ORA}
\subsection{Concatenable traces}
\begin{lemma}
	\todo{abstract equivalence and switch }
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}
\begin{definition}
	\todo{tracce}
\end{definition}

@@

\appendix
\section{A note on fillers and sequential independence}\label{app:fill}
 In \Cref{prop:equi} we proved that, in the linear case, the existence of an indpendence pair between two derivation is equivalent to that of a filler between them. This result can be further refined: in a\cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi)adhesive category is defined for which the local Church-Rosser Theorem holds even for left-linear DPO-rewriting system. In our language, and given \Cref{prop:fil} and \Cref{rem:locCR}, this amount to prove that, for elements of $\mathbb{B}$, every independence pair induces a filler.

>>>>

\begin{remark}\label{rem:inversa}
Let $\sigma:[0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$: indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
\end{remark}

@@

@@

\begin{lemma} Let $(\X,R)$ be a left-linear DPO-rewriting system. Consider two consistent permutation $\sigma,\sigma':[0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$. Suppose that $\sigma\neq \sigma'$ and let $j$ be the minimum index such that $\sigma(j)\neq \sigma'(j)$. Let also $r(\der{D})$ be $\{\rho_i\}_{i=0}^n$. Then the following hold true:
	\begin{enumerate}
		\item if $j=0$, then the rule $\rho_0$ is not consuming;
		\item if $j\neq 0$ then the rule $\rho_{j-1}$ is not consuming.
	\end{enumerate}
\end{lemma}
\begin{proof}\begin{enumerate}
		\item Let $k$ be $\sigma^{-1}(\sigma'(0))$ and notice that, since $\sigma(0)\neq \sigma'(0)$, then $0< k$.  By  the first point of  \Cref{prop:uniqu} we can consider the diagram
		\[\xymatrix@C=40pt{& L_0 \ar[d]_{m'_{\sigma'(0)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{0}} \\G_{0} \ar@/_.2cm/[drr]_(.3){\iota_{G_0}}|(.515)\hole \ar[d]_{\iota_{G_0}}& G'_{\sigma'(0)} \ar[d]^{\iota_{G'_{\sigma'(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
	From \Cref{cor:ele}, we can conclude that there exists $c:L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
		\[\xymatrix{L_0 \ar@/^.3cm/[drr]^{\id{L_0}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_0 \ar[d]_{k_0}\ar[r]^{l_0}& L_0 \ar[d]^{m_0} \\& D_0 \ar[r]_{f_0} & G_0} \]
		The internal square is an $\mathcal{M}$-pushout and thus a pullback, by \Cref{prop:pbpoad}, so that we have the existence of the dotted $t:L_0\to K_0$. Therefore $\id{L_0}=l_0\circ t$, proving that $l_0$ is an epimorphism. The thesis now follows from \Cref{cor:rego}.  
		\item  Let $k$ be $\sigma^{-1}(\sigma'(j-1))$ and notice that $\rho_{j-1}=\rho_k$. By definition of $j$, $\sigma_{|[0,j-1]}=\sigma'_{|[0,j-1]}$, thus the second point of \Cref{prop:unique} yields the diagram
			\[\xymatrix@C=40pt{& L_{j-1} \ar[d]_{m'_{\sigma'(j-1)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{j-1}} \\G_{j-1} \ar@/_.2cm/[drr]_(.3){\iota_{G_{j-1}}}|(.515)\hole \ar[d]_{\iota_{G_{j-1}}}& G'_{\sigma'(j-1)} \ar[d]^{\iota_{G'_{\sigma'(j-1)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c:L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
			\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar[r]_{f_a} & G_a} \]
			The existence of the dotted $t:L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qed
	\end{enumerate}
\end{proof}

\begin{corollary}\label{cor:unique}
Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming. For every two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, there exists at most one consistent permutation between them.
\end{corollary}

\begin{corollary}\label{cor:dec}
	\todo{prefisso e suffisso}
\end{corollary}
\begin{proof}
	contenuto...\qed 
\end{proof}

@@

\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists. If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
\end{definition}

@@

\begin{example}
	\todo{pensare ad un esempio in cui l'indipendenza non basta }
\end{example}

@@

We can prove some other properties of the arrows appearing in the diagram above. The three rectangles below are pushouts and their left halves are pushouts too. Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{g}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j'}&Q' \ar[r]^{t} & T}\]

Notice, moreover, that $p, q$ are the pushouts of $l'$ and $l$, respectively, thus they  are elements of $\mathcal{M}$. By \Cref{prop:pbpoad} the squares
\[\xymatrix{P\ar[r]^{p} \ar[d]_{p'} & D \ar[d]^{g}& P \ar[r]^{p} \ar[d]_{q} &D\ar[d]^{f}\\ D' \ar[r]_{f'} & H & Q \ar[r]_{s}& G}\]
are pullbacks too.
\end{remark}

@@

	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
\begin{definition}\label{def:switch}
	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive. Given two switchable direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, with a filler $(u,u')$, we can define other two direct derivations $S_{u,u'}(\dder{D}'):G\Mapsto J$ and $S_{u,u'}(\dder{D}):J\Mapsto T$ as follows:
		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{u,u'}(\dder{D}')\cdot S_{u,u'}(\dder{D})$.
\end{definition}

@@

\subsection{Proper switchability is global}
\todo{intro}

\begin{lemma}[Invariance under immediate shift, 1] Let $(\X,\R)$ be a left-linear DPO-rewriting system consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$. If $(v,v')$ is a filler between $\dder{D}_0$ and $\dder{D}_1$, $(u,u')$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{u,u'}(\dder{D}_2)$ with filler $(w,w')$, then there exists a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$.
\end{lemma}
\begin{proof}
By \Cref{def:filler,def:switch}, the fillers $(v,v')$, $(u,u')$ and $(w,w')$ give us the following three diagrams 
			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
			\[\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){g_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]

		To construct a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$,  we can start pulling back $x_2:Q_3\to G'_2$, which is in $\mathcal{M}$, along $z'_1:Q_5\to G'_2$ along  to get the solid part of the diagram below.
			\[\xymatrix{&&R_0 \ar@{.>}@/_1cm/[ddrr]_(.25){\alpha_1}|(.7)\hole  \ar[dr]^{\hspace{-4pt}g_1\circ e_0}&& L_1\ar@{.>}@/^1cm/[ddll]^(.25){\alpha_2}  \ar[dl]_{y_1\circ b_1\hspace{-4pt}}\\&K_0\ar[dr]^{n_1\circ w}\ar[dl]_{l_0} \ar@{.>}@/_.8cm/[ddrr]_(.65){\beta}\ar[ur]^{r_0}&& G'_2&& K_1 \ar@{.>}@/^.8cm/[ddll]^(.65){\beta'}\ar[dl]_{d_2\circ u}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar[dr]_{z'_0\circ o_0} && Q_5 \ar[dl]|(.4)\hole_(.6){z_1}\ar[ur]|(.5)\hole^(.7){z'_1}&&Q_3 \ar[dr]|(.4)\hole^(.65){y_2} \ar[ul]|(.5)\hole_(.7){x_2}&&R_1\ar@{.>}@/^.8cm/[ddll]^{\gamma'}\ar[dl]_(.4){g_2\circ a_1}\\&G'_1 &&P_4\ar@{.>}[dr]^{\epsilon'} \ar[ur]^(.4){\delta'}\ar[ul]_(.4){\delta}&&G_2\\&& &&Q_6}\]

		Let us construct the dotted arrows.
		\begin{itemize}
		\item Existence of $\beta$. Comsider the arrows $i_0\circ r_0:K_0\to D_1$ and $u_1\circ w:K_0\to Q_2$. Then
		\begin{align*}
	f_1\circ i_0\circ r_0&=h_0\circ r_0\\&=g_0\circ k_0\\&=g_0\circ u_0\circ w\\&=x_1\circ u_1\circ w
		\end{align*}
		\item Existence of $\beta'$. We proceed as above, this time taking the arrows $i_1\circ l_1:K_1\to D_0$ and $d_1\circ u:K_1\to Q_2$. We get
		\begin{align*}
			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=f_1\circ k_1\\&f_1\circ c_1\circ u\\&=x_1\circ d_1\circ u
		\end{align*}
		giving a unique $\underline{\beta}':K_1\to P_3$ fitting in the diagram 
		\[\xymatrix{K_1 \ar@{.>}[dr]^{\underline{\beta}'} \ar[r]^{l_1} \ar[d]_{u}& L_1 \ar@/^.2cm/[dr]^{i_1}\\ P_2 \ar@/_.2cm/[dr]_{d_1}&P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\]
		If we compute we get
		\begin{align*}
			z'_1\circ n_1\circ\underline{\beta}'&=y_1\circ u_1\circ \underline{\beta}'\\&=y_1\circ d_1\circ u\\&=x_2\circ d_2\circ u
		\end{align*}
		Therefore there is $\beta':K_1\to P_4$ such that
		\[\xymatrix{K_1 \ar@{.>}[dr]^{\beta'} \ar[r]^{\underline{\beta}'} \ar[d]_{u}& P_3 \ar@/^.2cm/[dr]^{n_1}\\ P_2 \ar@/_.2cm/[dr]_{d_2}&P_4 \ar[r]^{\delta} \ar[d]_{\delta'}& Q_5 \ar[d]^{z'_1}\\ &Q_3\ar[r]_{x_2} & G'_2}\]
		commutes.
		\item Existence of $\alpha_1$.
		\item Existence of $\alpha_2$.
		\item Existence of $\epsilon'$.
		\item Existence of $\gamma'$.
		\end{itemize}

		Finally, we have to show that these data form a filler.
	\begin{enumerate}
		\item 
		\item 
	\end{enumerate} 
\end{proof}

\begin{lemma}[Invariance under immediate shift, 2]\todo{nell'altro senso}
\end{lemma}
\begin{proof}
 \todo{fare} \qed 
\end{proof}

\begin{corollary}
\todo{passare a $\updownarrow_!$ e $\Updownarrow$}
\end{corollary}

\todo{ricopiare tutta l'induzione di Andrea}
\subsection{Concatenable traces}
\begin{lemma}
	\todo{abstract equivalence and switch }
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}
\begin{definition}
	\todo{tracce}
\end{definition}

@@

\appendix
\section{On permutations}\label{app:perm}
\todo{inserire risutati sulle permutazione che abbiamo usato}

\section{A note on fillers and sequential independence}\label{app:fill}
 In \Cref{prop:equi} we proved that, in the linear case, the existence of an indpendence pair between two derivation is equivalent to that of a filler between them. This result can be further refined: in a\cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi)adhesive category is defined for which the local Church-Rosser Theorem holds even for left-linear DPO-rewriting system. In our language, and given \Cref{prop:fil} and \Cref{rem:locCR}, this amount to prove that, for elements of $\mathbb{B}$, every independence pair induces a filler.
